### 2019-03-13 paper/sex_selection_spacing-ver2.tex
Initial work on distribution of spacing results

\subsection{How the Distribution of Birth Spacing Varies Across Sex Compositions and Time}

Median spacing is a convenient way to understand the overall changes but
may hide important differences in the distribution of spacing.
This section, therefore, provides more detail on how spacing is distributed
over time and sex compositions using a graphical approach.%
\footnote{
Furthermore, Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
\ref{tab:p25_p75_high} show 25th, 50th, and 75th percentiles durations with
bootstrapped standard errors.
}

I show survival curves conditional on predicted parity progression rather than
standard survival curves. 
The advantage of this approach is that it is possible to directly compare 
the distribution of spacing to next birth across groups, independently of 
differences in how likely the next birth is.
Because the conditional survival curves are independent of the likelihood
of final parity progression, they all begin at 100\% and end at 0\%.

Instead of averaging across the entire sample, I calculate the conditional
survival curves for an average woman using the method detailed in 
Section \ref{sec:strategy}.
For each combination of education and spell, I use values based on the
average age at the start of the spell and, for the second and higher
spells, the average duration of the first spell.
Furthermore, I use the majority categories for the categorical explanatory 
variables, which means no ownership of land and not in a scheduled caste or 
tribe.
The characteristics used do not change across period to ensure that 
composition effects do not drive the changes.

In the interest of brevity, I discuss only a select set of subsamples.
Figure \ref{fig:pps_spell1} shows spacing for the first spell across the
four periods for rural women with no education and urban women with 
eight or more years of education.
Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex
compositions for the second, third, and fourth spells for the first period, 
1972--1984, and the last period, 2005--2016, for rural women with no 
education and for urban women with eight or more years of education.
The Appendix shows standard and conditional survival curves for all groups and 
time periods, and I discuss some examples of standard survival
curves in the following section.%
\footnote{
To ease legibility of the graphs some three months intervals are combined
into longer ones when there are few births available in the sample.
}

@@

The biased sex ratio for the first spell for the most educated 
women suggests that there might be sex selection on the first birth.
I, therefore, begin by comparing in Figure \ref{fig:pps_spell1} how the distribution 
of spacing has changed over time for rural women with no education and urban women 
with eight or more years of education.
What is most striking is how similar the distribution of spacing is across the
two groups.

Both groups show little change in median spacing, but that masks a substantial
compression of when most of the births occur.
In the 1972--1984 period, the middle 80\% of births for women with no education 
are predicted to occur between approximately 6 and 64 months, whereas in the 
2005--2016 period it is between 12 and 54 months.
Hence, the compression is equivalent to more than a full year.
Women with eight or more years of education show a slightly smaller compression:
in the 1972--1984 period, the middle 80\% of births are predicted to occur between
approximately 6 and 48 months, whereas in the 2005--2016 period it is between
12 and 46 months.
Hence, the compression is eight months.

Women became less likely to conceive before marriage over time.
In the first two periods there was a relatively smooth decline in the number of
women without a birth starting at the time of marriage, but in the last two
periods, there are few women who exit early after marriage and
instead there is a substantial dip between 9 and 12 months after
marriage.

It is likely that the compressed spacing, beginning at nine months
after marriage in the later periods, is associated with better health
and higher age at marriage.
For example, women without education have seen an increase in the average 
age at marriage from below 16 to 18.5 from the first period to the last 
while women with the most education increased from 19.5 to 20.4.

@@

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{1}
\subfloat[1995--2005]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[1985--1994]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{5}
\subfloat[1995--2004]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[2005--2016]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with no education by month beginning 9 months after prior birth.
}
\label{fig:results_spell2_low_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - LOW

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{1}
\subfloat[1995--2004]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{5}
\subfloat[1995--2004]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[2005--2016]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with no education by month beginning 9 months after prior birth.
}
\label{fig:results_spell3_low_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - LOW

\begin{figure}[htpb]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{1}
\subfloat[1995--2004]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{5}
\subfloat[1995--2004]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[2005--2016]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with no education by month beginning 9 months after prior birth.
}
\label{fig:results_spell4_low_pps}
\end{figure}

>>>>

\subsection{Distribution of Birth Spacing Within Spells and Across Sex Compositions}

Average spacing is a convenient way to understand the overall changes but may hide 
important differences in the distribution of spacing.
Specifically, a concern is that the increases in average spacing that I show above may 
mask an increased variance in birth spacing with families with fewer sons both more likely 
to have a very pregnancy and to continue through pregnancies and sex-selective abortions 
until they conceive a son.
This section, therefore, provides more detail on how spacing is distributed within a spell 
and across sex compositions using a graphical approach.

I show survival curves conditional on predicted parity progression rather than standard 
survival curves. 
The advantage of this approach is that it is possible to directly compare the distribution 
of spacing to next birth across groups, independently of differences in how likely the 
next birth is.
Because the conditional survival curves are independent of the likelihood of parity 
progression within the spell, they all begin at 100\% and end at 0\%.

Instead of averaging across the entire sample, I calculate the conditional survival curves 
for an average woman using the method detailed in Section \ref{sec:strategy}.%
\footnote{
To complement this approach, Appendix Tables \ref{tab:p25_p50_p75_low}, 
\ref{tab:p25_p50_p75_med}, and \ref{tab:p25_p50_p75_high} show 25th, 50th, and 75th 
percentiles durations with bootstrapped standard errors based on averages across all women 
in the each subsample as for the results above.
} 
For each combination of education and spell, I use values based on the average age at the 
start of the spell.
Furthermore, I use the majority categories for the categorical explanatory  variables, 
which means no ownership of land and not in a scheduled caste or tribe.
The characteristics used do not change across the four decades to ensure that composition 
effects do not drive any changes.

In the interest of brevity, I discuss only a select set of subsamples.
Figures \ref{fig:pps_low} and \ref{fig:pps_high} show spacing across sex compositions for 
the second, third, and fourth spells for the first period, 1972--1984, and the last 
period, 2005--2016, for rural women with no education and for urban women with eight or 
more years of education.
The Appendix shows conditional survival curves for all groups and decades.

@@

% The biased sex ratio for the first spell for the most educated 
% women suggests that there might be sex selection on the first birth.
% I, therefore, begin by comparing in Figure \ref{fig:pps_spell1} how the distribution 
% of spacing has changed over time for rural women with no education and urban women 
% with eight or more years of education.
% What is most striking is how similar the distribution of spacing is across the
% two groups.
% 
% Both groups show little change in median spacing, but that masks a substantial
% compression of when most of the births occur.
% In the 1972--1984 period, the middle 80\% of births for women with no education 
% are predicted to occur between approximately 6 and 64 months, whereas in the 
% 2005--2016 period it is between 12 and 54 months.
% Hence, the compression is equivalent to more than a full year.
% Women with eight or more years of education show a slightly smaller compression:
% in the 1972--1984 period, the middle 80\% of births are predicted to occur between
% approximately 6 and 48 months, whereas in the 2005--2016 period it is between
% 12 and 46 months.
% Hence, the compression is eight months.
% 
% Women became less likely to conceive before marriage over time.
% In the first two periods there was a relatively smooth decline in the number of
% women without a birth starting at the time of marriage, but in the last two
% periods, there are few women who exit early after marriage and
% instead there is a substantial dip between 9 and 12 months after
% marriage.
% 
% It is likely that the compressed spacing, beginning at nine months
% after marriage in the later periods, is associated with better health
% and higher age at marriage.
% For example, women without education have seen an increase in the average 
% age at marriage from below 16 to 18.5 from the first period to the last 
% while women with the most education increased from 19.5 to 20.4.

@@

% Low education
\vspace*{-0.75cm}
\begin{figure}[hp!]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{1}
\subfloat[1995--2005]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g1_low_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[1985--1994]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g2_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{5}
\subfloat[1995--2004]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g3_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[2005--2016]{
    \begin{minipage}{0.32\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell2_g4_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with no education by month beginning 9 months after prior birth.
}
\label{fig:results_spell2_low_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - LOW
\vspace*{-0.75cm}
\begin{figure}[hp!]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{1}
\subfloat[1995--2004]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g1_low_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g2_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{5}
\subfloat[1995--2004]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g3_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[2005--2016]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell3_g4_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with no education by month beginning 9 months after prior birth.
}
\label{fig:results_spell3_low_pps}
\end{figure}

@@

% PARITY PROGRESSION SURVIVAL - LOW
\vspace*{-0.75cm}
\begin{figure}[hp!]
\centering
\caption*{Urban}
\setcounter{subfigure}{-1}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-0}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{1}
\subfloat[1995--2004]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{2}
\subfloat[2005--2016]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_urban_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{Rural}
\setcounter{subfigure}{3}
\subfloat[1972--1984]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_pps}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{4}
\subfloat[1985--1994]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} \\
\setcounter{subfigure}{5}
\subfloat[1995--2004]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[2005--2016]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g4_low_rural_pps}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Survival curves conditional on parity progression
for women with no education by month beginning 9 months after prior birth.
}
\label{fig:results_spell4_low_pps}
\end{figure}
